\section{PHP}

Acrónimo recursivo de PHP: Pre Hypertext Preprocessor.  Es un lenguaje de código abierto muy popular especialmente adecuado para el desarrollo web y que puede ser incrustado en HTML. Se ejecuta del lado del servidor generando HTML y enviándolo al cliente.

\subsection{Printing}

\begin{itemize}
	\item echo: it command allows to print several results. \textit{echo: $""$, $""$;}
	\item print: it command  allows to print one result at a time. \textit{print: "";}
\end{itemize}


\subsection{Variables}

The name of the variable must begin with \$ simbol.
\begin{itemize}
	\item \$numeric = 5;
	\item \$text = "string";
	\item \$booleana = true;
	\item \$arrays = array($"element1","element2"$); to index the array it must be used squared pharentesis and the index begins in zero.
	\item \$objects= (object)[$"element1"=>"value1","element2"=>"value2"$]; to access de object objects=>elemen1
\end{itemize}

\subsection{Methods}

\begin{itemize}
	\item var\_dump(variable) the method allows to know the type of variable it's being used and the content or variable length.
\end{itemize}

\subsection{Functions}
The sintaxes of a function is
\begin{lstlisting}[language=PHP]
function (parameters){
    return var;
}
\end{lstlisting}

\subsection{Conditionals}
The sintaxes of a conditional is
\begin{lstlisting}[language=PHP]
if(condition){
    code
}else if(condition){
    code
}else{
    code
}
\end{lstlisting}

The sintaxes of a switch case is

\begin{lstlisting}[language=PHP]
switch(varCase){
    case :
    break;
	
    case :
    break;
	
    default:
    break;
}
\end{lstlisting}

\subsection{cycles}

The sintaxes of a while cycle is

\begin{lstlisting}
while(condition){
    code
}
\end{lstlisting}

The sintaxes of a do while cycle is

\begin{lstlisting}
do{
    code
}while(condition);
\end{lstlisting}

The sintaxes of a for cycle is

\begin{lstlisting}
for($i=0; $i<5; $i++){
    code
}
\end{lstlisting}

